\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Paper Précis: Creating a Shared Understanding of Testing Culture on a Social Coding Site}

### 2014-11-20 article_2.tex
WIP

@@

\subsection{Interaction on GitHub with Regard to Testing}

This section reports on our findings regarding the contribution process on GitHub and how project owners assess pull requests from contributors (RQ 1.1).
In the course of our interviews, several steps of the contribution process on GitHub emerged. After receiving a pull request, the first step that project owners conducted was to manually review the contribution and assess it by different
aspects. After this review, they merged the pull request into a testing branch and resolved conflicts manually. Superficial adjustments like code style corrections or comments were added based on preference. If a test suite existed, project owners ran it to check whether or not this contribution passed tests. This increased confidence in the contribution. Finally, the contribution was merged into the main branch of the project.
We found many factors that were taken into consideration by project owners when assessing contributions. For instance, project owners reported to treat incoming pull requests differently depending on whether they trusted the contributing developer. Pull requests from unknown developers would undergo a more thorough assessment, while contributions from trusted developers would be merged right away. ?if it?s someone I trust, who?s worked on the project a lot, then I don?t do that. [...] if it?s someone who hasn?t spent a lot of time on the project, I?ll try and do that.? [L48]
The perceived size of the changes highly influenced the project owner?s need for tests. If the project owner believed to have quickly understood the changes? impact, they demanded no tests from the contributor. This was often the case when only some lines of code had been changed.
Additionally, project owners distinguished between two types of contributions: contributions that introduced a new feature or contributions that changed existing code, such as bug fixes. The former were requested to include tests, while the latter caused project owners to check whether or not the changed code was already covered by existing tests. If so, no further tests were demanded. ?if you really write a new feature, then it makes more sense to add tests for that, but if you just do a little change in a code chunk that is already there then I don?t expect that the person writes the test for that.? [FI19]
The target of the changes was considered as well. Changes to core functionality caused a demand for tests. However, if the estimated effort for creating automated tests was regarded as infeasible, this demand was waived. Often, such tests would require a cumbersome setup of test environments (such as different operating systems). Project owners were aware that contributors acted voluntarily and were unfunded in most cases.

\subsection{Motivations for Demanding and Delivering Tests}

This section presents our findings regarding project owners? motivations for demanding tests and contributors? motivations for providing them (RQ 1.2).
Project owners? reasons for demanding tested contributions were manifold. Maintaining clean and well documented code reduced the subsequent support effort, according to one project owner. Some project owners perceived tests as a form of documentation of how to use the contributed feature. Another project owner requested contributors to provide test cases of how they needed the software to behave, so he could merge these into the existing test suite for future regression testing. In this case, tests were used for communicating requirements.
An external motivator was the impression of acting as a role model when working on a testing-related project. Several users reported to feel obliged to perform proper quality assurance for projects with a domain related to testing ? e.g. a testing framework or a continuous integration server.
In interviews with contributors, different motivations for including tests in a pull request on one?s own initiative emerged. Some interviewees said they explicitly added tests that highlight the value of their contribution to the project owner: these tests failed with the old version of the software in question, but passed when the contribution was applied.
The existence and prominent placement of tests gave contributors the impression of informal project guidelines; thus they felt obligated to add their own tests. ?[There were no guidelines set up], not so much formally, but it was pretty clear how it was supposed to be tested and there was already an existing spec file [...] with a pretty substantial list of tests? [FI17]
Similar to a project owner perceiving oneself as a role model when working on a testing-related project, contributors felt an implicit demand for tested pull requests in such domains. In other instances, this obligation also resulted from customs rooted in the community of the technology used. Often, Ruby developers tested their contribution by default.

@@

In section V, we presented findings gathered by conducting 33 interviews with GitHub users. This section presents the most striking results of our final questionnaire (Q2) that we used to validate core statements of our findings. Of 4,000 random GitHub users, 569 filled out this questionnaire. Our results are summarized in Table I. PO denotes statements about project owners, C about contributors. For each question, we presented the participant with a Likert scale of five items ranging from ?I do not agree at all? to ?I strongly agree.?. These Likert items are represented in the diagrams on the X- axis with disagreement being on the left and agreement being on the right hand-side. The middle bar represents the neutral item. The number of answers accumulated for each Likert item is marked on the Y-axis. The grey bar is the median.
The questionnaire required the participant to take both the perspective of a project owner and a contributor. 39\% of our participants would receive pull requests at least a few times per week (daily: 16\%) and 27\% send pull requests at least a few times per week (daily: 6\%). Even though several interviewees mentioned voluntarism as a hindering factor, the questionnaire did not validate this (PO1). Personal traits such as modesty and humility of the requester as well as value given to the contribution may be influencing factors. Similarly, most of the participants did not agree to feel a need for automation (PO2). However, as some interviewees mentioned, this need may depend on the size and popularity of the project in question. As popularity grows, the amount of incoming pull requests increases. As both samples were randomly invited, but ultimately self-selected, variations in populations might attribute for this dissonance.
Project owners agree that providing tests in one?s project lowers the support effort regarding testing by contributors (PO3). Appropriately, contributors heavily rely on existing test cases when creating their own. They use these to learn how testing is done in a specific project (C3) and, lastly, even copy existing tests and use them as a basis for new tests (C4). With tests in place, contributors feel obligated to add their own tests and seem to comply with this implicit demand (C2).

\section{Discussion}
This section relates our work to previous research and discusses its potential impact on the software development industry, open source development, and research. We connect our findings with research in Communities of Practice and the diffusion of innovations. In doing so, we distinguish between processes occurring inside of projects ? intra-project ? and those spanning multiple projects, i.e., inter-project processes.

\subsection{Creating a Shared Understanding}

Lave and Wenger [24] coined the term Community of Practice (CoP) for groups of individuals that work on sim- ilar problems and exchange knowledge about good practices, proven solutions, etc. with each other. They mention legiti- mate peripheral participation as a central phenomenon when describing how new members of the CoP join and, through learning the community?s norms, become more and more involved with it. Initially, novices merely observe practices passively before starting to take on simple and increasingly complex tasks. New members are said to be situated in the community?s periphery, while established members are part of the core. As shown by Crowston et al. [16], these processes can apply to open source software development as well.

\subsection{Diffusion of Testing Practices}

GitHub does not only help Communities of Practice create a shared understanding of their respective testing culture in peripheral and novice contributors. It also facilitates the dif- fusion of these practices among developers inside and outside of individual communities.
Research on the diffusion of innovations investigates how and why tools, practices, ideas, or technologies perceived as new ? innovations ? are adopted by individuals and groups. Rogers [25] documents properties of innovations that were discovered to support their adoption across many different scenarios.
? Relative Advantage: adoption is more likely if the in- novation has a clear advantage with regard to known alternatives.
? Compatibility: the more compatible an innovation is to a person?s existing practices, the more likely it is that she will adopt it.
? Complexity: the more complex an innovation is perceived to be, the less likely it will be adopted.
? Observability: an innovation will be more likely to be adopted the easier it is to observe existing adopters.
? Trialability: the easier it is to try out an innovation before deciding to adopt it, the more likely it is to be adopted.

>>>>

\usepackage{graphicx}
\usepackage{float}

@@

\textbf{\textit{Interaction on GitHub with Regard to Testing:}} The interview process presented several common steps in the GitHub contribution process. After receiving a pull request (PR), a project owner manually reviews the contribution and assess it by different
aspects. Following such, they merged the PR into a testing branch and resolved conflicts manually. If a test suite existed, owners ran it to check whether or not this contribution passed. Finally, the contribution was merged into the main branch of the project. 
\par
It emerged that many factors that were taken into consideration by owners when assessing contributions, such are as follows: 
\begin{itemize}
\item \textbf{Contribution Size:} the perceived size of the changes highly influenced the project owner's need for tests.
\item \textbf{Developer Trust:} owners treated incoming PRs differently depending on whether they trusted the contributing developer.
\item \textbf{Contribution Type:} owners had different testing approaches for contributions that introduced a new feature and contributions that changed existing code. The former were requested to include test whereas the latter caused project owners to check whether or not the changed code was already covered by existing tests. 
\end{itemize} 
\par

\textbf{\textit{Motivations for Demanding \& Delivering Tests:}} Project owners' reasons for demanding tested contributions were manifold. Maintaining clean and well documented code reduced the subsequent support effort, according to one project owner.

Some project owners perceived tests as a form of documentation of how to use the contributed feature. Another project owner requested contributors to provide test cases of how they needed the software to behave, so he could merge these into the existing test suite for future regression testing. In this case, tests were used for communicating requirements.
An external motivator was the impression of acting as a role model when working on a testing-related project. Several users reported to feel obliged to perform proper quality assurance for projects with a domain related to testing ? e.g. a testing framework or a continuous integration server.
In interviews with contributors, different motivations for including tests in a pull request on one?s own initiative emerged. Some interviewees said they explicitly added tests that highlight the value of their contribution to the project owner: these tests failed with the old version of the software in question, but passed when the contribution was applied.
The existence and prominent placement of tests gave contributors the impression of informal project guidelines; thus they felt obligated to add their own tests. ?[There were no guidelines set up], not so much formally, but it was pretty clear how it was supposed to be tested and there was already an existing spec file [...] with a pretty substantial list of tests? [FI17]
Similar to a project owner perceiving oneself as a role model when working on a testing-related project, contributors felt an implicit demand for tested pull requests in such domains. In other instances, this obligation also resulted from customs rooted in the community of the technology used. Often, Ruby developers tested their contribution by default.

@@

This section poses striking results from the final questionnaire (Q2) which was used to validate core statements of Pham's findings. The according results are summarised in Table I, where C  illustrates statements about contributors and PO about project owners. 
For each question, we presented the participant with a Likert scale of five items ranging from ?I do not agree at all? to ?I strongly agree.?. These Likert items are represented in the diagrams on the X- axis with disagreement being on the left and agreement being on the right hand-side. The middle bar represents the neutral item. The number of answers accumulated for each Likert item is marked on the Y-axis. The grey bar is the median.
\begin{table}[H]
  \centering
  	\caption{Result of final questionnaire (Q2)}
	\includegraphics[width=77mm, height=150mm]{qa2.png}
\end{table}

The questionnaire required the participant to take both the perspective of a project owner and a contributor. 39\% of our participants would receive pull requests at least a few times per week (daily: 16\%) and 27\% send pull requests at least a few times per week (daily: 6\%). Even though several interviewees mentioned voluntarism as a hindering factor, the questionnaire did not validate this (PO1). Personal traits such as modesty and humility of the requester as well as value given to the contribution may be influencing factors. Similarly, most of the participants did not agree to feel a need for automation (PO2). However, as some interviewees mentioned, this need may depend on the size and popularity of the project in question. As popularity grows, the amount of incoming pull requests increases. As both samples were randomly invited, but ultimately self-selected, variations in populations might attribute for this dissonance.
Project owners agree that providing tests in one?s project lowers the support effort regarding testing by contributors (PO3). Appropriately, contributors heavily rely on existing test cases when creating their own. They use these to learn how testing is done in a specific project (C3) and, lastly, even copy existing tests and use them as a basis for new tests (C4). With tests in place, contributors feel obligated to add their own tests and seem to comply with this implicit demand (C2).
